My title

### 2024-02-14 paper/paper.qmd
Refactored cleaning script

```{r}
#| echo: false
#| include: false

#### Load Data ####
incentive_data <-
  read_csv(
    file = "../data/analysis_data/food_data.csv",
    show_col_types = FALSE,
    # skip = 1
  )

# Filter data for only public treatment tables
public_data <- incentive_data|>
  filter(private == 0)

#https://tellingstorieswithdata.com/11-eda.html#united-states-population-and-income-data
incentive_data_sum <-
incentive_data |>
  as_tibble() |>
  mutate(state = rownames(incentive_data)) |>
  select(public, incentive, table_incentive_pr, table_size, male, black, grade, hispanic, free)

# Change all column contains '999' to NA
incentive_data_sum[incentive_data_sum == 999] <- NA

```{r}
#| echo: false
#| include: false

# Public-0-no incentive: Children in the public treatment in which none of the grape cards were incentivized.
public_0_no_incentive <- incentive_data_sum |>
  filter(public == 1 & table_incentive_pr == 0)

# Calculate mean values for each numeric column excluding NAs
#https://www.r-bloggers.com/2023/07/exploring-data-with-colmeans-in-r-a-programmers-guide/
mean_values <- colMeans(public_0_no_incentive, na.rm = TRUE)

# Round mean values to two decimal places
mean_values <- round(mean_values, 2)

# Get the total number of rows
total_rows <- nrow(public_0_no_incentive)

# Create a new data frame with the mean values and total rows
sum_table <- data.frame(
  Group = 'Public-0',
  Variable = names(mean_values),
  Mean = mean_values,
  Observations = total_rows
)
sum_table_wide <- pivot_wider(sum_table, names_from = "Variable", values_from = "Mean")

```{r}
#| echo: false
#| include: false

# Public-50-no incentive: Children in the public treatment in which 50 percent of the grape cards were incentivized, and the child’s own card was not incentivized. 
public_50_no_incentive <- incentive_data_sum %>%
  filter(public == 1 & table_incentive_pr > 0 & table_incentive_pr < 1  & incentive == 0)

# Calculate mean values for each numeric column excluding NAs
mean_values <- colMeans(public_50_no_incentive, na.rm = TRUE)

# Round mean values to two decimal places
mean_values <- round(mean_values, 2)

# Get the total number of rows
total_rows <- nrow(public_50_no_incentive)

# Create a new data frame with the mean values and total rows
sum_table <- data.frame(
  Group = 'Public-50-no incentive',
  Variable = names(mean_values),
  Mean = mean_values,
  Observations = total_rows
)

sum_table <- pivot_wider(sum_table, names_from = "Variable", values_from = "Mean")

# Append sum_table to sum_table_wide
sum_table_wide <- rbind(sum_table_wide, sum_table)

```{r}
#| echo: false
#| include: false

# Public-50-incentive: Children in the public treatment in which 50 percent of the grape cards were incentivized, and the child’s own card was incentivized
Public_50_incentive <- incentive_data_sum %>%
  filter(public == 1 & table_incentive_pr > 0 & table_incentive_pr < 1  & incentive == 1)

# Calculate mean values for each numeric column excluding NAs
mean_values <- colMeans(Public_50_incentive, na.rm = TRUE)

# Round mean values to two decimal places
mean_values <- round(mean_values, 2)

# Get the total number of rows
total_rows <- nrow(Public_50_incentive)

# Create a new data frame with the mean values and total rows
sum_table <- data.frame(
  Group = 'Public-50-incentive',
  Variable = names(mean_values),
  Mean = mean_values,
  Observations = total_rows
)

sum_table <- pivot_wider(sum_table, names_from = "Variable", values_from = "Mean")

# Append new_data to sum_table_wide
sum_table_wide <- rbind(sum_table_wide, sum_table)

```{r}
#| echo: false
#| include: false

# Public-100-incentive: Children in the public treatment in which all of the grape cards were incentivized.
Public_100_incentive <- incentive_data_sum %>%
  filter(public == 1 & table_incentive_pr == 1 & incentive == 1)

# Calculate mean values for each numeric column excluding NAs
mean_values <- colMeans(Public_100_incentive, na.rm = TRUE)

# Round mean values to two decimal places
mean_values <- round(mean_values, 2)

# Get the total number of rows
total_rows <- nrow(Public_100_incentive)

# Create a new data frame with the mean values and total rows
sum_table <- data.frame(
  Group = 'Public-100-incentive',
  Variable = names(mean_values),
  Mean = mean_values,
  Observations = total_rows
)

sum_table <- pivot_wider(sum_table, names_from = "Variable", values_from = "Mean")

# Append new_data to sum_table_wide
sum_table_wide <- rbind(sum_table_wide, sum_table)

```{r}
#| echo: false
#| include: false

combined_table <- rbind(public_0_no_incentive, public_50_no_incentive, Public_50_incentive, Public_100_incentive)

mean_values <- colMeans(combined_table, na.rm = TRUE)

# Round mean values to two decimal places
mean_values <- round(mean_values, 2)

# Get the total number of rows
total_rows <- nrow(combined_table)

# Create a new data frame with the mean values and total rows
sum_table <- data.frame(
  Group = 'Total',
  Variable = names(mean_values),
  Mean = mean_values,
  Observations = total_rows
)

sum_table <- pivot_wider(sum_table, names_from = "Variable", values_from = "Mean")

# Append new_data to sum_table_wide
sum_table_wide <- rbind(sum_table_wide, sum_table)

@@

@@

>>>>

@@

sum_table_wide <-
  read_csv(
    file = "../data/analysis_data/sum_table_wide.csv",
    show_col_types = FALSE
  )

@@

public_data <-
  read_csv(
    file = "../data/analysis_data/public_data.csv",
    show_col_types = FALSE
  )
